---
title: "R Notebook"
output: html_notebook
---

You have been provided some customer data from a shopping centre. Do some exploratory analysis on the data. Comment on findings.

```{r}
library(tidyverse) #load libraries first
library(cluster)
library(factoextra)
library(dendextend)
library(janitor)
```

```{r}
mall_customers <- read_csv("mall_customers.csv") #import dataset
head(mall_customers)
```

```{r}
glimpse(mall_customers)
```

```{r}
class(mall_customers)
```

```{r}
any(is.na(USArrests)) #check for missing values
```

No NA values, this is good news. Now we need to tidy the dataframe

```{r}
mall_tidy <- clean_names(mall_customers) %>%
  select(- customer_id) #remove as this does not give additional information
 mall_tidy
```

#Lets try a few plots to see how they compare

```{r}
mall_tidy %>%
  select(c(annual_income_k, spending_score_1_100))

ggplot(mall_tidy, aes(annual_income_k, spending_score_1_100)) +
  geom_point()
```
#This looks very messy, there is a cluster of data in the middle which appears to branch out in an x shape

There are a few variables so use gg pairs


```{r}
library(GGally)
 mall_tidy %>%
  select(gender, age, annual_income_k, spending_score_1_100) %>%
  ggpairs()
```

There are not much clear correlations here, perhaps age and spending score shows a bit more promise.

We are interested in creating a marketing campaign to target customers based on their spending score and annual income. Perform a k-means clustering to find if there are meaningful clusters in the data to target the customers.

```{r}
mall_tidy_scale <- mall_tidy %>% 
  select(annual_income_k, spending_score_1_100) %>% 
                      mutate_all(scale)

summary(mall_tidy_scale)
```

Check each of the methods of choosing k:

Elbow method

```{r}
fviz_nbclust(mall_tidy_scale, kmeans, method = "wss", nstart = 25)
```

Fairly smooth, maybe k =5 is where there is more of a kink, potentially k = 3 also

Slhouette coefficient

```{r}
fviz_nbclust(mall_tidy_scale, kmeans, method = "silhouette", nstart = 25)
```

k = 5 chosen above although k= 7 is also close to average width

Gap statistic

```{r}
fviz_nbclust(mall_tidy_scale, kmeans, method = "gap_stat")
```

Here k=1 showing. This is different to the above tests indicating that this data may not be well suited for k-means clustering.

However I would go with the sihouette method as it looks similar to the elbow method, at k = 5.

Visualise the clustering for your chosen value of k.

```{r}
clustered_mall_tidy <- kmeans(mall_tidy_scale, 5, nstart = 25)

clustered_mall_tidy
```

```{r}
clusters <- augment(clustered_mall_tidy, mall_tidy)

ggplot(clusters, aes(x = annual_income_k,
                     y = spending_score_1_100, colour = .cluster)) +
  geom_point() 
```

Do you think the clustering seems a good fit for this data?

Yes, this creates 5 distinct clusters for the data, clusters 1 and 5 are very close however overall the groups are distinct.

Comment on the attributes on one or two of the clusters (maybe even give them a label if you like - like in section 4.1 of the ‘Segmentation & clustering intro’ lesson).

Cluster 5 appears a good one to use for the campaign since the data points are very close together. The next best option would appear to be cluster 2.

