---
title: "R Notebook"
output: html_notebook
---

```{r}
library(prob)
library(gtools)
library(tidyverse)
```

1. If I roll a six-sided dice once, what is the probability of getting a number less than 5?

```{r}
rolldie(1)
```
```{r}
single_die <- rolldie(1) %>%
  filter(X1 < 5)
single_die
```
```{r}
nrow(single_die)/nrow(rolldie(1))
```
The above, or more precisely 4/6 or 2/3




2. How many outcomes are there in the sample space of an experiment in which we toss three dice?

```{r}
rolldie(3)
```

Or could have worked this out as 6 x 6 x 6 = 216


3. In an experiment where we roll four dice:
how many outcomes are in the event total_equals_5_6_7 (i.e. the total of the four dice equals 5, 6 or 7)?
what is the probability of this event?
what assumptions do we apply in answering part ii?
Hint
For part i, rowSums(.) may help you setup up the necessary random variable

```{r}
sumdie <- rolldie(4) %>%
filter((X1 + X2 + X3 + X4) <= 7) #Minus one figure, as 1 combination is 4, the rest 5 plus
 sumdie
```

Total = 35-1 = 34 rows (subtracting the 1 value of 1 + 1 + 1 + 1 = 4) There maybe is an easy way to check if the sum is equal to 5 6 or 7 however I could not find it.

Probability of this = events/total = 34/(6 x 6 x 6 x 6) = 
                                   = 34/1296
                                   = 0.026
                                   
                                    
```{r}
34/nrow(rolldie(4))
```
We are making the assumption that the dice are fair (equal chance of falling on any side each)


4. Five chairs are placed in a row in a room, along with five people of differing height. The people sit down randomly on the chairs. What is the probability that they sit in order of decreasing height, left to right?

Hint
This is an arrangement where order matters. Of all the possible arrangements, how many are correct? 
First find number of permutations (order is important) we know it's 1 out of this.
The answer is 5! = 5 x 4 x 3 x 2 x 1 = 120, (remember nPr = n!/(n -r)! where n, r =5 and 0! =1, so permuatations is always factorial of objects where n = r  but let's check using R code.

```{r}
heights <- c("shortest", "short", "medium", "tall", "tallest") 

five_height_permutations <- permutations (n = 5,
                                          r = 5,
                                          v = heights, 
                                          repeats.allowed = FALSE)
five_height_permutations
```

```{r}
1/120
```
 Or 1/120 is the probability.




5. I roll six dice:

what is the probability I see the numbers 6, 5, 4, 3, 2 and 1 in order on the dice, left to right?
what is the probability I see one each of the numbers 6, 5, 4, 3, 2 and 1 on the dice regardless of order?
[Hint have a look at the isin() function in the prob package. For example, to filter all rows containing 6, 1, 2 in that order, you could use isin(., c(6, 1, 2), ordered = TRUE)]

Just like the last question there is only one probability for this in this particular order so the answer is = 1/(6 x 6 x 6 x 6 x 6 x 6) = 1/46656 = 0.0000214

```{r}
six_dice_in_order <- rolldie(6) %>%
  filter(X1 == 1 & X2 == 2 & X3 == 3 & X4 == 4 & X5 == 5 & X6 == 6) 
six_dice_in_order
```

```{r}
nrow(rolldie(6))
```

So answer = 
```{r}
1/nrow(rolldie(6))
```

Now for 6, 5, 4, 3, 2, 1 regardless of the order we use combination (order is not important)
The solution is 6!/(6-6)! = 720/1 = 720

```{r}
six_dice_different_values <- rolldie(6) %>%
  filter(isin(., c(1, 2, 3, 4, 5, 6), ordered = FALSE))
six_dice_different_values
```


6. If I draw a single card from a 52-card deck, and it is black, what is the probability that its suit is spades?

Hints
Investigate the cards() function in the prob package, if you’d like to try this in R (make a deck without jokers).
You could think about adding your own black_card random variable to the sample space, which would be TRUE if the suit is ‘Spade’ or ‘Club’, and FALSE otherwise.

I'll try without R first. Answer is 1 in 2, or 0.5, since half the balck suits are spades.
Using conditional probability, this is P(A|B) = P(AnB)/P(B)
                                              =(13/52)/(26/52)
                                              = 13/26
                                              = 1/2
Now I'll try the cards package

```{r}
cards()
```

```{r}
black_card <- cards() %>%
  filter(suit == "Spade")
  black_card
```

As expected, 13 rows out of 26 (Clubs have 13 cards also)






7. Eight patients: Alice, Bob, Carmen, Dinesh, Ella, Fergus, Gianna and Henry are waiting to see a doctor, but only five appointment slots are left today.

In how many different orders can the doctor see patients today?

Answer = this is a permutation because the order is important at this point, 5 out of the 8 get to the doctors in any order. 
nPr = n!/(n - r)
    = 8!/3!
    = 8 x 7 X 6 x 5 x 4
    = 6720

```{r}
the_waitful_eight <- c("Alice", "Bob", "Carmen", "Dinesh", "Ella", "Fergus", "Gianna", "Henry") 

only_five_arrive <- as_tibble(permutations(n = 8,
                                 r = 5,
                                 v = the_waitful_eight, 
                                          repeats.allowed = FALSE)
  ) 
only_five_arrive
```



8. If order is not significant, how many ways are there to select a 5 student quiz team from a group of 8 students?








9. (harder) How would your answer for question 8 change if a team captain had to be selected for each team?









10. The following data from a sample of 120 families shows the record of university attendance by mothers and their eldest sons.

in 32 families, both the mother and son attended university;
in 31 families, neither the mother nor the son attended university
in 22 families, the mother attended university while the son did not
in 35 families, the son attended university while the mother did not.
Arrange the data above in a convenient dataframe and answer the following questions:

What is the probability that a son attended university given that his mother attended university?
What is the probability that a son attended university given that his mother did not attend university?
Is attending university by the son independent of whether his mother attended university?



