---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

1 Load the diamonds.csv data set and undertake an initial exploration of the data. You will find a description of the meanings of the variables on the relevant Kaggle page

```{r}
diamonds <- read_csv("diamonds.csv")
summary(diamonds)
names(diamonds)
glimpse(diamonds)
```

2. We expect the carat of the diamonds to be strong correlated with the physical dimensions x, y and z. Use ggpairs() to investigate correlations between these four variables.

```{r}
diamonds_4_var <- diamonds %>%
  select(c("carat", "x", "y", "z"))
glimpse(diamonds_4_var)
```


```{r}
library(GGally)
ggpairs(diamonds_4_var)
```

3 So, we do find significant correlations. Let’s drop columns x, y and z from the dataset, in preparation to use only carat going forward.

```{r}
diamonds_1_var <- diamonds_4_var %>%
  select(c("carat"))
glimpse(diamonds_1_var)
```

4. We are interested in developing a regression model for the price of a diamond in terms of the possible predictor variables in the dataset.
Use ggpairs() to investigate correlations between price and the predictors (this may take a while to run, don’t worry, make coffee or something).

```{r}
diamonds_5_var <- diamonds %>%
  select(c("price", "carat", "x", "y", "z"))
glimpse(diamonds_5_var)
```

```{r}
ggpairs(diamonds_5_var)
```

It looks like price increases more with x and carat, although a lot of the data looks lumped together

ii Perform further ggplot visualisations of any significant correlations you find.

```{r}
diamonds_5_var %>%
  ggplot(aes(x = x, y = price, group = 1)) + 
  geom_boxplot()
```

```{r}
diamonds_5_var %>%
  ggplot(aes(x = carat, y = price, group = 1)) + 
  geom_boxplot()
```

5. Shortly we may try a regression fit using one or more of the categorical predictors cut, clarity and color, so let’s investigate these predictors:
Investigate the factor levels of these predictors. How many dummy variables do you expect for each of them?

```{r}
diamonds %>%
levels(cut)
levels(clarity)
levels(color)
 #Error below, not sure why?
```

