---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(modelr)
library(ggiraphExtra)
library(GGally)
```


```{r}
kc_house_data <- read_csv("kc_house_data.csv")
summary(kc_house_data)
names(kc_house_data)
glimpse(kc_house_data)
head(kc_house_data)
```

Lets take out unnecessary columns

```{r}
kc_house_trim <- kc_house_data %>%
  select(-c(id, date, sqft_living15, sqft_lot15, zipcode))
glimpse(kc_house_trim)
```

Lets check waterfront
```{r}
unique(kc_house_trim$waterfront) #Only 0 and 1, convert to yes or no
```

Convert watertype to true/false
```{r}
kc_house_logical <- kc_house_trim %>%
  mutate(waterfront = as.logical(waterfront)) %>%
  mutate(yr_renovated = as.logical(yr_renovated))
kc_house_logical 
```

Lets check condition and grade to see the data types

```{r}
 unique(kc_house_logical$condition)  
```
#The above is ordinal data

```{r}
unique(kc_house_logical$grade) 
```
#The above is categorical ordinal

Check for aliased variables using the alias() function

```{r}
alias( lm(price ~ bedrooms)$kc_house_logical )
```

Now lets try first predictor
```{r}
kc_house_logical  %>%
  ggpairs(aes(colour = yr_renovated, alpha = 0.5))
```

Lets try splitting this to numeric/ non numeric to save loading time

```{r}
houses_tidy_numeric <- kc_house_logical %>%
  select_if(is.numeric)

houses_tidy_nonnumeric <- kc_house_logical %>%
  select_if(function(x) !is.numeric(x))

houses_tidy_nonnumeric$price <- kc_house_logical$price

ggpairs(houses_tidy_numeric)
ggpairs(houses_tidy_nonnumeric)
```

Try first model

```{r}
mod1a <- lm(price ~ sqft_lot, data = kc_house_logical)
mod1a
```

```{r}
summary(mod1a)
```

```{r}
par(mfrow = c(2, 2)) 

# plot
plot(mod1a)
```

