---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(infer)
```


```{r}
ames <- read_csv("ames.csv")
```

```{r}
clean_ames <- clean_names(ames)
clean_ames
```

```{r}
glimpse(clean_ames)
```

```{r}
names(clean_ames)
```

```{r}
dim(clean_ames)
```

```{r}
clean_ames %>%
  ggplot(aes(x = lot_area)) +
  geom_histogram(col = "white", fill = "steel blue", alpha = 0.7)
```

This distribution is not normal. There is a significant count of zero values for area (which should not be the case). Although it look binomial it is skewed to the right.

I'm checking first that all the houses were actually sold
```{r}
clean_ames %>%
  select(order, sale_price) %>%
arrange(sale_price)
```

```{r}
bootstrap_ames <- clean_ames %>%
  rep_sample_n(size = 500, replace = TRUE, reps = 5000) %>%
  summarise(mean_lot_area = mean(lot_area))
bootstrap_ames
```

```{r}
bootstrap_ames %>%
  ggplot(aes(x = mean_lot_area)) +
  geom_histogram(col = "white", fill = "steel blue", alpha = 0.7)
```


```{r}
infer_ames <- clean_ames %>%
  specify(response = lot_area) %>%
  generate(reps = 5000, type = "bootstrap") %>%
  calculate(stat = "mean")
infer_ames
```


```{r}
infer_ames_95 <- infer_ames %>%
  get_ci(level = 0.95, type = "percentile")
infer_ames_95
```

```{r}
infer_ames %>%
  visualise() +
  shade_confidence_interval(endpoints = infer_ames_95)
```

```{r}
infer_ames_99 <- infer_ames %>%
  get_ci(level = 0.99, type = "percentile")
infer_ames_99
```

```{r}
infer_ames %>%
  visualise() +
  shade_confidence_interval(endpoints = infer_ames_99)
```

We see above in the figures and the graph the CI is wider. Of course, this makes sense as for us to have more confidence there must be a greater range we can choose from.

Lets check point estimate

```{r}
infer_ames %>%
  summarise(mean(stat))
```

Now compare with mean of original sample for completeness

```{r}
clean_ames %>%
  summarise(mean(lot_area))
```

