---
title: "R Notebook"
output: html_notebook
---

# Ensure libraries containing functions you want are imported
```{r}
library(tidyverse)
library(dplyr)
```
#Conflicts showing above, however this will not matter for the purposes of this dataset

#Below ensure data is read in

```{r}
starbucks_menu <- read_csv("data/starbucks_drinkMenu_expanded.csv")
```

Question 1
Load in the dataset and have a look at it. What are the dimensions, variable types, variable names, etc.?
```{r}
dim(starbucks_drinkMenu_expanded)
# overall dimensions
```


```{r}
# classes (ie: varchar, boolean)
class(starbucks_drinkMenu_expanded)
```


```{r}
# variable names
names(starbucks_drinkMenu_expanded)
```


```{r}
# number of rows
nrow(starbucks_drinkMenu_expanded)
```


```{r}
# number of observations
ncol(starbucks_drinkMenu_expanded)
```

```{r}
# get an overview of the data 
glimpse(starbucks_drinkMenu_expanded)
```


Question 2
Let’s first investigate the calories of different drinks. Select the variables Beverage_category, Beverage, Beverage prep and Calories from your data. Since we are interested in the calorie content, check if there are any NA values in the data, and drop them if there are.

```{r}
#assigning a name to the new tibble with a few categories
different_drinks <- select(starbucks_drinkMenu_expanded, Beverage_category, Beverage, Beverage_prep, Calories) 
different_drinks
```

#Identifying NA 

```{r}
#This isn't right, I'm trying to show values where they are null
glimpse(different_drinks, var = "na")
```


```{r}
#Drop any na function
different_drinks_no_na <- drop_na(different_drinks)

different_drinks_no_na
```


Question 3
Create a new variable (column) called calorie_diff, which stores the difference between 135 calories (135 calories = 10 cubes of sugar!) and the calories in each drink. (hint: you’ll want to subtract the calories from 135 to see which drink have more or less than 10 cups of sugar).

```{r}
starbucks_bonus_data <- mutate(starbucks_drinkMenu_expanded, calorie_diff = 135 - Calories)
starbucks_bonus_data
#It's the last category on the right
```


Question 4
Summarise the mean number of calories in each beverage_category. Which 3 drinks have the most calories? Which 3 drinks have the least? Write a small summary of your findings.

```{r}
# group the starbucks data by beverage
calories_group <- group_by(starbucks_drinkMenu_expanded, Beverage)

# print the tibble out, and here you'll see at the top the number of groups you have created: 
calories_group_mean_pipe <- calories_group %>%
  select(mean(calories_group)) %>%
  arrange(desc(mean(calories_group))) %>%
 calories_group_mean_pipe
 limit==3 %>%
   
  calories_group_mean_pipe 
  
#Not sure how to fix this
#Now I need to print out the mean
```


Question 5
Let’s look at this a different way. What is the average number of calories in each Beverage_prep type?

```{r}

starbucks_drinkMenu_expanded %>% 
  select(Calories) # need to have beverage prep here
  group_by(Beverage_prep) %>%
    #summarise(mean_cals = mean(Calories)) %>%
    #arrange(desc(mean_cals))
  mutate(mean == (Calories/sum(Calories))) 
  
```



Question 6
Which Beverage_prep type contains more than the average calories of all drinks?
Hint: to answer this, you’ll have to first figure out what the average calories across all drinks are, and then use that as a filter for the grouped Beverage_prep data.

```{r}
average_calories <- mean(drink_calories$Calories)
#Need to do avg_calories <- mean(drink_calories$Calories)

above_avg_calories <- average_bev_prep %>%
  filter(mean_cals >= avg_calories)


```





Question 7
Which is the best type of coffee drink to get if you’re worried about consuming too many calories?

Brewed coffee. Unless Tazo tea co
```{r}
```













